---
title: "FYP_project_4_sketching"
author: "Nicolaj Valsted"
date: "23/4/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Exercises 28/04


### Exercise 1

```{r}
dat1 <- data.frame(x = rep(c("a", "", "b", ""), times = c(1,2,1,2)),
                   y = LETTERS[1:3], z = "hep", stringsAsFactors = FALSE)
dat2 <- data.frame(x = letters[2:4],
                   y = "A", w = 1:3, stringsAsFactors = FALSE)
```


```{r}
dat1
```

```{r}
dat2
```

```{r}
dat1 <- mutate(dat1, x= na_if(x,""))
dat1 <- fill(dat1, x, .direction = "down")
```

```{r}
dat1
```

### Exercise 2

```{r}
left_join(dat1, dat2, by = c("x","y"))
```

### Exercise 3

```{r}
full_join(dat1, dat2, by = c("x","y"))
```

### Exercise 4

### a.
Combinations of storkreds, opstillingskreds and valgdistrikt.

### b.
For the FV19TOTA dataset, these are nested in column B. For the PollingDistrictCharacteristics dataset, there is a column dedicated to each of the three variables to make up a unique ID, which makes it already ready for joining. 

### c.
The nesting in the FV19TOTA dataset needs to be unravelled before joining with the PollingDistrictCharacteristics dataset.

### Exercise 5

```{r}
afstemningsomraader <- read_sf("E:/pile_of_data/FYP4/DAGI/dagi_10m_nohist_l1.afstemningsomraade/afstemningsomraade.shp")

noerrebro_opstilling <- filter(afstemningsomraader,opstilling == "5")
noerrebro_opstilling
```

```{r}
noerrebro_opstilling$points <- st_point_on_surface(noerrebro_opstilling)
noerrebro_opstilling$coords <- as.data.frame(st_coordinates(noerrebro_opstilling$points))

ggplot() +
  geom_sf(data = noerrebro_opstilling, size = 0.5) +
  geom_label(data = noerrebro_opstilling, aes(coords$X,coords$Y,label=navn),size=3) +
  annotation_scale(location = "bl", width_hint = 0.4) +
  xlab("Longitude") + ylab("Latitude") +
  ggtitle("Denmark",subtitle = "landsdele") 
```

### Exercise 6

```{r}
noerrebro_opstilling$centroid <- st_centroid(noerrebro_opstilling)
noerrebro_opstilling
```

### 7

```{r}
ggplot() +
  geom_sf(data = noerrebro_opstilling, size = 0.5) +
  geom_sf(data = noerrebro_opstilling$centroid, size = 4, aes(color = navn)) +
  #geom_label(data = noerrebro_opstilling, aes(coords$X,coords$Y,label=navn),size=3) +
  annotation_scale(location = "bl", width_hint = 0.4) +
  xlab("Longitude") + ylab("Latitude") +
  ggtitle("Denmark",subtitle = "landsdele") 
```



## Task 2 sketching

```{r}
library("ggplot2")
theme_set(theme_bw())
library("sf")
library("ggspatial")
library("UsingR")
library("rmarkdown")
library("grid")
library("dplyr")
library("tidyr")
```

```{r}
map_landsdele <- read_sf("E:/pile_of_data/FYP4/DAGI/dagi_10m_nohist_l1.landsdel/landsdel.shp")

map_landsdele$area <- as.numeric(st_area(map_landsdele))

```

```{r}
map_landsdele
```


```{r}
ggplot() +
  geom_sf(data = map_landsdele, size = 0.5) +
  scale_fill_viridis_c(trans = "sqrt", alpha = .4) +
  ggtitle("Bornholm") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        plot.title  = element_text(size = 8)) +
  coord_sf(xlim = c(855000, 900000), ylim = c(6105000, 6150000), expand=FALSE)
```

```{r}
main_plot <- ggplot() +
  geom_sf(data = map_landsdele, size = 0.5, aes(fill = area)) +
  scale_fill_viridis_c(trans = "sqrt", alpha = .4) +
  annotation_scale(location = "bl", width_hint = 0.4) +
  xlab("Longitude") + ylab("Latitude") +
  ggtitle("Denmark",subtitle = "landsdele") +
  coord_sf(xlim = c(420000, 750000), ylim = c(6030000, 6420000), expand=FALSE)

bornholm_plot <- ggplot() +
  geom_sf(data = map_landsdele, size = 0.5) +
  scale_fill_viridis_c(trans = "sqrt", alpha = .4) +
  ggtitle("Bornholm") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        plot.title  = element_text(size = 8)) +
  coord_sf(xlim = c(855000, 900000), ylim = c(6105000, 6150000), expand=FALSE)

vp <- viewport(width = 0.2, height = 0.2, x = 0.725, y = 0.8)

pdf("Map_draft.pdf")

print(main_plot)
print(bornholm_plot, vp=vp)

dev.off()
```

