---
title: "work_on_4_part_2"
author: "dffdfd"
date: "5/5/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(sf)
library(ggplot2)
library(xlsx)
library(dplyr)
library(tidyr)
library(tidyverse)
library(gridExtra)
library(gtable)
library(grid)
library(tmap)
```

```{r}
map_data <- read_sf("C:/Users/andre/OneDrive/Documents/ITU/fyp/4/DAGI/dagi_10m_nohist_l1.landsdel/landsdel.shp")
map_data <- summarise(group_by(map_data, navn))
map_data <- mutate(map_data, navn = na_if(navn, "Vest- og Sydsjælland"))
map_data <- mutate(map_data, navn = na_if(navn, "Østsjælland"))
map_data <- mutate(map_data, navn = replace_na(navn, "Sjælland"))
map_data <- summarise(group_by(map_data, navn))
map_data


mandat_data <- read.xlsx2("C:/Users/andre/OneDrive/Documents/ITU/fyp/4/mandater.xlsx",1,stringsAsFactors = FALSE)
mandat_data <- filter(mandat_data, Mandater != "-")
mandat_data$Mandater <- as.integer(mandat_data$Mandater)
mandat_data <- mutate(mandat_data, navn = na_if(navn, ""))
mandat_data <- fill(mandat_data, navn, .direction = "down")
mandat_data

map_data_2 <- left_join(map_data, mandat_data, by = "navn")
map_data_2
```


```{r}
ggplot(map_data) + geom_sf(aes(fill=navn)) + xlab("longtitude") + ylab("lattitude") + ggsave("plot.png", width = 1, height = 1)
```













Background layer (using map_data)


```{r}
map_data_3 <- map_data_2
# 1. make new column that has "red" if red party and "blue" if blue party
map_data_4 <- filter(map_data_3, Partier == "A. Socialdemokratiet" | Partier == "B. Radikale Venstre" | Partier == "F. SF - Socialistisk Folkeparti" | Partier == "Ø. Enhedslisten" | Partier == "Å. Alternativet")
map_data_4 <- mutate(map_data_4, block = "red")
map_data_4 <- summarise(group_by(map_data_4, navn, Partier, block))
map_data_4 <- st_drop_geometry(map_data_4)
map_data_3 <- left_join(map_data_3, map_data_4, by = c("navn", "Partier"))
map_data_3 <- mutate(map_data_3, block = replace_na(block, "blue"))
map_data_3

# 2. add the mandates for each "navn" for each of the blocks
map_data_3$block_mandates <- ave(map_data_3$Mandater, map_data_3$navn, map_data_3$block, FUN=sum)
map_data_3

# 3. remove the party-names column
map_data_3 <- summarise(group_by(map_data_3, navn, block, block_mandates))
map_data_3

# 4. check whether the blue block or the red block has won that "storkreds" or if it is a tie and add the result to a new column
winner_map_data <- map_data_3

winner_map_data$winning_mandates_number <- ave(winner_map_data$block_mandates, winner_map_data$navn, FUN=max)
winner_map_data <- mutate(winner_map_data, winning_block = identical(block_mandates, winning_mandates_number))
winner_map_data <- filter(winner_map_data, winning_block == TRUE)
winner_map_data <- summarise(group_by(winner_map_data, navn, block))

#hvis 2 rækker i træk har samme værdi i 'navn', så replace TRUE med 'tie':
checkker <- summarise(group_by(winner_map_data, navn), tie = n()>1)
checkker <- st_drop_geometry(checkker)
winner_map_data <- left_join(winner_map_data, checkker, by = "navn")

replace_tie <- filter(winner_map_data, tie == TRUE)
replace_tie <- mutate(replace_tie, winner = "tie")
replace_tie <- st_drop_geometry(replace_tie)


# 5. add this new column to map_data
winner_map_data <- left_join(winner_map_data, replace_tie, by = "navn")
winner_map_data <- summarise(group_by(winner_map_data, navn, block.x, winner))
winner_map_data <- mutate(winner_map_data, winner = replace_na(winner, block.x))
winner_map_data <- summarise(group_by(winner_map_data, navn, winner))
winner_map_data
```







```{r}
winner_map <- ggplot(winner_map_data) + geom_sf(aes(fill=winner)) + scale_fill_manual(values=c("blue", "red", "yellow")
) + xlab("longtitude") + ylab("lattitude") + ggsave("winner_map.png", width = 6, height = 6)
winner_map
```


```{r}
winner_map <- ggplot(winner_map_data) + geom_sf(aes(fill=winner)) + scale_fill_manual(values=c("blue", "red", "yellow")
) + xlab("longtitude") + ylab("lattitude") + ggsave("winner_map2.png", width = 10, height = 10)
```


```{r}
map_data_2 <- mutate(map_data_2, geometry = st_centroid(geometry))
map_data_2
```





```{r}
ggplot(winner_map_data) + geom_sf(aes(fill=winner)) + scale_fill_manual(values=c("blue", "red", "yellow")
) + xlab("longtitude") + ylab("lattitude") + geom_sf(data = map_data_2) + ggsave("background_map_dots.png")
```


```{r}
map_data_2
```

```{r}
bornholm_data <- filter(map_data_2, navn == "Bornholm")
byen_kobenhavn_data <- filter(map_data_2, navn == "Byen København")
fyn_data <- filter(map_data_2, navn == "Fyn")
kobenhavns_omegn_data <- filter(map_data_2, navn == "Københavns omegn")
nordjylland_data <- filter(map_data_2, navn == "Nordjylland")
nordsjaelland_data <- filter(map_data_2, navn == "Nordsjælland")
ostjylland_data <- filter(map_data_2, navn == "Østjylland")
sjaelland_data <- filter(map_data_2, navn == "Sjælland")
sydjylland_data <- filter(map_data_2, navn == "Sydjylland")
vestjylland_data <- filter(map_data_2, navn == "Vestjylland")
```


```{r}
byen_kobenhavn_data
```

1

```{r}
bornholm_data <- bornholm_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(bornholm_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
bornholm_pie_chart <- ggplot(bornholm_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Bornholm") + ggsave("Bornholm_pie_chart.png")
bornholm_pie_chart
```

2

```{r}
byen_kobenhavn_data <- byen_kobenhavn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(byen_kobenhavn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
byen_kobenhavn_pie_chart <- ggplot(byen_kobenhavn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Byen København") + ggsave("byen_kobenhavn_pie_chart.png")
byen_kobenhavn_pie_chart
```


Alternativet = "green" 
Socialdemokratiet = "#CC0000"
Radikale venstre = "#FF3399"
Konservative = "dark green"
SF = "#FF6666" 
Liberal alliance = "orange" 
Dansk Folkeparti = "#000099" 
Enhedslisten = "#FF0000" 
Venstre = "#6699FF"



3

```{r}
fyn_data <- fyn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(fyn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
fyn_pie_chart <- ggplot(fyn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Fyn") + ggsave("fyn_pie_chart.png")
fyn_pie_chart
```

4

```{r}
kobenhavns_omegn_data <- kobenhavns_omegn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(kobenhavns_omegn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
kobenhavns_omegn_pie_chart <- ggplot(kobenhavns_omegn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Københavns Omegn") + ggsave("kobenhavns_omegn_pie_chart.png")
kobenhavns_omegn_pie_chart
```

5

```{r}
nordjylland_data <- nordjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordjylland_pie_chart <- ggplot(nordjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Nordjylland") + ggsave("nordjylland_pie_chart.png")
nordjylland_pie_chart
```

6

```{r}
nordsjaelland_data <- nordsjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordsjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordsjaelland_pie_chart <- ggplot(nordsjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Nordsjælland") + ggsave("nordsjælland_pie_chart.png")
nordsjaelland_pie_chart
```

7

```{r}
ostjylland_data <- ostjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(ostjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
ostjylland_pie_chart <- ggplot(ostjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Østjylland") + ggsave("ostjylland_pie_chart.png")
ostjylland_pie_chart
```

8

```{r}
sjaelland_data <- sjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sjaelland_pie_chart <- ggplot(sjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Sjælland") + ggsave("sjaelland_pie_chart.png")
sjaelland_pie_chart
```

9

```{r}
sydjylland_data <- sydjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sydjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sydjylland_pie_chart <- ggplot(sydjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Sydjylland") + ggsave("sydjylland_pie_chart.png")
sydjylland_pie_chart
```

10

```{r}
vestjylland_data <- vestjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(vestjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
vestjylland_pie_chart <- ggplot(vestjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Vestjylland") + ggsave("vestjylland_pie_chart.png")
vestjylland_pie_chart
```


bornholm_data <- filter(map_data_2, navn == "Bornholm")
byen_kobenhavn_data <- filter(map_data_2, navn == "Byen København")
fyn_data <- filter(map_data_2, navn == "Fyn")
kobenhavns_omegn_data <- filter(map_data_2, navn == "Københavns omegn")
nordjylland_data <- filter(map_data_2, navn == "Nordjylland")
nordsjaelland_data <- filter(map_data_2, navn == "Nordsjælland")
ostjylland_data <- filter(map_data_2, navn == "Østjylland")
sjaelland_data <- filter(map_data_2, navn == "Sjælland")
sydjylland_data <- filter(map_data_2, navn == "Sydjylland")
vestjylland_data


```{r}
bornholm_data <- bornholm_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(bornholm_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
bornholm_pie_chart <- ggplot(bornholm_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

byen_kobenhavn_data <- byen_kobenhavn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(byen_kobenhavn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
byen_kobenhavn_pie_chart <- ggplot(byen_kobenhavn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

fyn_data <- fyn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(fyn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
fyn_pie_chart <- ggplot(fyn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

kobenhavns_omegn_data <- kobenhavns_omegn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(kobenhavns_omegn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
kobenhavns_omegn_pie_chart <- ggplot(kobenhavns_omegn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

nordjylland_data <- nordjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordjylland_pie_chart <- ggplot(nordjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

nordsjaelland_data <- nordsjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordsjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordsjaelland_pie_chart <- ggplot(nordsjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

ostjylland_data <- ostjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(ostjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
ostjylland_pie_chart <- ggplot(ostjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

sjaelland_data <- sjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sjaelland_pie_chart <- ggplot(sjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

sydjylland_data <- sydjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sydjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sydjylland_pie_chart <- ggplot(sydjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

vestjylland_data <- vestjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(vestjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
vestjylland_pie_chart <- ggplot(vestjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)



g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(ostjylland_pie_chart)

p3 <- grid.arrange(arrangeGrob(
  bornholm_pie_chart + theme(legend.position="none") + labs(caption = "Bornholm"), 
  byen_kobenhavn_pie_chart + theme(legend.position="none") + labs(caption = "Byen København"),
  fyn_pie_chart + theme(legend.position="none") + labs(caption = "Fyn"), 
  kobenhavns_omegn_pie_chart + theme(strip.text = , legend.position="none") + labs(caption = "Københavns Omegn"), 
  nordjylland_pie_chart + theme(legend.position="none") + labs(caption = "Nordjylland"), 
  nordsjaelland_pie_chart + theme(legend.position="none") + labs(caption = "Nordsjælland"), 
  ostjylland_pie_chart + theme(legend.position="none") + labs(caption = "Østjylland"), 
  sjaelland_pie_chart + theme(legend.position="none") + labs(caption = "Sjælland"), 
  sydjylland_pie_chart + theme(legend.position="none") + labs(caption = "Sydjylland"), 
  vestjylland_pie_chart + theme(legend.position="none") + labs(caption = "Vestjylland"),
                         nrow=5),
             mylegend, ncol=2,heights=c(75, 1), widths=c(1,1))
```



```{r}
bornholm_data <- bornholm_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(bornholm_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
bornholm_pie_chart <- ggplot(bornholm_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#6699FF"))

byen_kobenhavn_data <- byen_kobenhavn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(byen_kobenhavn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
byen_kobenhavn_pie_chart <- ggplot(byen_kobenhavn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF"))

fyn_data <- fyn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(fyn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
fyn_pie_chart <- ggplot(fyn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF"))

kobenhavns_omegn_data <- kobenhavns_omegn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(kobenhavns_omegn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
kobenhavns_omegn_pie_chart <- ggplot(kobenhavns_omegn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF"))

nordjylland_data <- nordjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordjylland_pie_chart <- ggplot(nordjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF"))

nordsjaelland_data <- nordsjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordsjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordsjaelland_pie_chart <- ggplot(nordsjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF"))

ostjylland_data <- ostjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(ostjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
ostjylland_pie_chart <- ggplot(ostjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF"))

sjaelland_data <- sjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sjaelland_pie_chart <- ggplot(sjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF"))

sydjylland_data <- sydjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sydjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sydjylland_pie_chart <- ggplot(sydjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF"))

vestjylland_data <- vestjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(vestjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
vestjylland_pie_chart <- ggplot(vestjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF"))



g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(ostjylland_pie_chart)

p3 <- grid.arrange(arrangeGrob(
  bornholm_pie_chart + theme(legend.position="none") + labs(caption = "Bornholm"), 
  byen_kobenhavn_pie_chart + theme(legend.position="none") + labs(caption = "Byen København"),
  fyn_pie_chart + theme(legend.position="none") + labs(caption = "Fyn"), 
  kobenhavns_omegn_pie_chart + theme(strip.text = , legend.position="none") + labs(caption = "Københavns Omegn"), 
  nordjylland_pie_chart + theme(legend.position="none") + labs(caption = "Nordjylland"), 
  nordsjaelland_pie_chart + theme(legend.position="none") + labs(caption = "Nordsjælland"), 
  ostjylland_pie_chart + theme(legend.position="none") + labs(caption = "Østjylland"), 
  sjaelland_pie_chart + theme(legend.position="none") + labs(caption = "Sjælland"), 
  sydjylland_pie_chart + theme(legend.position="none") + labs(caption = "Sydjylland"), 
  vestjylland_pie_chart + theme(legend.position="none") + labs(caption = "Vestjylland"),
                         nrow=5),
             mylegend, ncol=2,heights=c(75, 1), widths=c(1,1))
```






```{r}
distortion_data <- map_data_2

distortion_data <- st_zm(distortion_data)

distortion_data_2 <- distortion_data
distortion_data_2$sum_mandates <- ave(distortion_data_2$Mandater, distortion_data_2$navn, FUN = sum)
distortion_data_2 <- summarise(group_by(distortion_data_2, navn, sum_mandates))

distortion_data_2
```


```{r}
OpK_cont <- cartogram_cont(distortion_data, "Mandater", itermax = 10)
```

```{r}
OpK_cont_2 <- cartogram_cont(distortion_data_2, "sum_mandates", itermax = 10)
```

```{r}
tm_shape(OpK_cont_2) + tm_polygons("sum_mandates", style= "jenks") +
  tm_layout(frame = FALSE, legend.position = c("right","top"))
```

^ do this with population aswell











```{r}
grid_arrange_shared_legend <-
  function(...,
           ncol = length(list(...)),
           nrow = 3,
           position = c("bottom", "right")) {
    
    plots <- list(...)
    position <- match.arg(position)
    g <-
      ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
    legend <- g[[which(sapply(g, function(x)
      x$name) == "guide-box")]]
    lheight <- sum(legend$height)
    lwidth <- sum(legend$width)
    gl <- lapply(plots, function(x)
      x + theme(legend.position = "none"))
    gl <- c(gl, ncol = ncol, nrow = nrow)
    
    combined <- switch(
      position,
      "bottom" = arrangeGrob(
        do.call(arrangeGrob, gl),
        legend,
        ncol = 1,
        heights = unit.c(unit(1, "npc") - lheight, lheight)
      ),
      "right" = arrangeGrob(
        do.call(arrangeGrob, gl),
        legend,
        ncol = 2,
        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
      )
    )
    
    grid.newpage()
    grid.draw(combined)
    
    # return gtable invisibly
    invisible(combined)
    
  }




grid_arrange_shared_legend(bornholm_pie_chart, byen_kobenhavn_pie_chart, fyn_pie_chart, kobenhavns_omegn_pie_chart, nordjylland_pie_chart, nordsjaelland_pie_chart, ostjylland_pie_chart, sjaelland_pie_chart, sydjylland_pie_chart, vestjylland_pie_chart)


#grid.arrange(bornholm_pie_chart, byen_kobenhavn_pie_chart, fyn_pie_chart, kobenhavns_omegn_pie_chart, nordjylland_pie_chart, nordsjaelland_pie_chart, ostjylland_pie_chart, sjaelland_pie_chart, sydjylland_pie_chart, vestjylland_pie_chart, nrow = 4)
```










ggplot(winner_map_data) + geom_sf(aes(fill=winner)) + scale_fill_manual(values=c("blue", "red", "yellow")
) + xlab("longtitude") + ylab("lattitude")

```{r}
winner_map + geom_sf(data = byen_kobenhavn_data) +
  geom_bar(aes(x="", y=prop, fill=Partier), data = byen_kobenhavn_data, stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF", "grey", "magenta", "black"))
```


```{r}
byen_kobenhavn_data
```



right now I am seeing if I can store the plots in a new column 
```{r}
byen_kobenhavn_data <- mutate(byen_kobenhavn_data, plot = kbh_pie_chart)
byen_kobenhavn_data
```





```{r}
ggplot(byen_kobenhavn_data, aes(x="", y=prop, fill=Mandater)) +
  geom_bar(stat="identity", width=1, color="white")
```


```{r}
# Create Data
data <- data.frame(
  group=LETTERS[1:5],
  value=c(13,7,9,21,2)
)

# Compute the position of labels
data <- data %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(data$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )

# Basic piechart
ggplot(data, aes(x="", y=prop, fill=group)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.position="none") +
  
  geom_text(aes(y = ypos, label = group), color = "white", size=6) +
  scale_fill_brewer(palette="Set1")
```


```{r}
ggplot(data, aes(x="", y=prop, fill=group)) +
  geom_bar(stat="identity", width=1, color="white")
```


Respect population density

```{r}

```

```{r}
# Get the shape file of Africa
library(maptools)
data(wrld_simpl)
afr=wrld_simpl[wrld_simpl$REGION==2,]
 
# We can visualize the region's boundaries with the plot function
plot(afr)

# We work with the cartogram library 
library(cartogram)
 
# construct a cartogram using the population in 2005
afr_cartogram <- cartogram(afr, "POP2005", itermax=5)
 
# This is a new geospatial object, we can visualise it!
plot(afr_cartogram)




library(cartogram)
library(maptools)
library(rgdal)

afr <- spTransform(wrld_simpl[wrld_simpl$REGION==2 & wrld_simpl$POP2005 > 0,], CRS("+init=epsg:3395"))
afr_sf <- st_as_sf(afr)
afr_sf
afr_sf_carto <- cartogram_cont(afr_sf, "POP2005", 3)
afr_sf_carto


par(mfcol=c(1,3))
plot(afr, main="original")
plot(afr_sf_carto, main="distorted (sp)")
plot(st_geometry(afr_sf_carto), main="distorted (sf)")
```


```{r}

```



foreground layer (using map_data_2)

```{r}
mandat_number_data <- mutate(map_data_2, )

```







Failed attempts:


1
```{r}
map_data_2[1]
```



```{r}

for(row in map_data_2["Partier"]){
  if (navn == "A. Socialdemokratiet" | navn == "B. Radikale Venstre" | navn == "F. SF - Socialistisk Folkeparti" | navn == "Ø. Enhedslisten" | navn == "Å. Alternativet"){
    #add "red" to list
  }
  
  print(row)
}

```

```{r}
map_data_3 <- mutate(map_data_3, block = function(x){
  if (navn == "A. Socialdemokratiet" | navn == "B. Radikale Venstre" | navn == "F. SF - Socialistisk Folkeparti" | navn == "Ø. Enhedslisten" | navn == "Å. Alternativet"){
    return("red")
  } else {
    return("blue")
  }
})
map_data_3
```



```{r}
ggplot(map_data_2["Partier"]) + geom_sf(aes(fill=Partier)) + xlab("longtitude") + ylab("lattitude")

```




2

```{r}
#sum_column <- function(data,x,y){
#  if (data[y] == "red"){
#    
#  }
#}

kobenhavn_data <- filter(map_data_3, navn == "Byen København")
#kobenhavn_data <- mutate(kobenhavn_data, winner = if)
kobenhavn_data
```



4
```{r}
#winner_map_data$winning_block_2 <- diff(as.numeric(winner_map_data$navn)) != 0


#winner_map_data <- mutate(winner_map_data, winning_block_2 = diff(winner_map_data$))


#winner_map_data <- winner_map_data %>% group_by(navn, block) %>% mutate(winning_block_2 = if_else(duplicated(block) == FALSE, 1, 0))

#map_data_3 <- mutate(map_data_3, winning_block_dplicated = if_else())


#map_data_3[!duplicated(map_data_3$navn), ]

#map_data_3 <- mutate(map_data_3, winning_block_dplicated =  duplicated(navn))

#map_data_3$winning_block <- if(duplicated(map_data_3$navn)){return "tie"}
```




noter til ting

```{r}
d <- data.frame(a = c("A", "B", "B", "C", "C", "D"), b = 1:6)
d
who.has.many <- d %>% group_by(a) %>% summarise(many = n()>1)
who.has.many
left_join(d, who.has.many, by = "a")


#Eller uden piping: checkker <- summarise(group_by(<dataframe>, <column>), <navn på ny column = n()>1)
#left_join(<dataframe>, checkker, by = "<column name>")
```



