---
title: "task2_sketching"
author: "Nicolaj Valsted"
date: "11/5/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library Imports

```{r,message = FALSE, warning = FALSE}
library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
theme_set(theme_bw())
library(sf)
library(ggspatial)
library(UsingR)
library(rmarkdown)
library(grid)
library(cartogram)
library(tmap)
library(maptools)
```

## Reading and processing raw data

### Load data

```{r,message = FALSE, warning = FALSE}
FV19TOTA <- read_excel("data/FV19TOTA.xlsx") # No external preprocessing has been done to the imported data
FV19TOTA <- FV19TOTA %>% rename("Party" = "Folketingsvalget 2019 efter valgresultat, område og tid",
                    "Area" = "...2",
                    "Votes" = "...3")
FV19TOTA$Votes <- as.integer(FV19TOTA$Votes)

characteristics_data <- read_excel("data/PollingDistrictCharacteristics.xlsx",skip=4)
```

### Fixing spelling inconsistencies

```{r}
name_mapping_from <- c("Dragør Skole",
                       "Sønderkærhallen",
                       "Fuglebjerg Hallen",
                       "Grønbro-Hallen",
                       "Montebello, Gurrevej 90",
                       "Ll. Næstved Skole-Karrebækvej",
                       "Kobberbakkeskolen Sct. Jørgens",
                       "Ll Næstved Skole-Herlufsholmve",
                       "Ll Næstved Skole - Hyllinge",
                       "Ll Næstved Skole - Karrebæk",
                       "Karlslundehallerne",
                       "Tunehallerne",
                       "Hundigehallen",
                       "Havdrup",
                       "Csv-Skolen",
                       "Kroggårdskolen",
                       "Rasmus Rask Skolen",
                       "Bjerreby",
                       "Skibethallen Nord",
                       "Grejsdalshallen Nord",
                       "Petersmindehallen Nord",
                       "Dgi-Huset Syd",
                       "Vindinghallen Syd",
                       "Csv Syd",
                       "Tilst Skole, Tilst",
                       "Lystrup Skole",
                       "Gjerlev Forsamlingshus",
                       "Asferg Forsamlingshus",
                       "Skovlunde Skole - Syd",
                       "Harmonien",
                       "Det Nordlige Strandområde",
                       "Det Sydlige Strandområde",
                       "Landet",
                       "Randbøl Nord",
                       "Løget Kirke Syd")

name_mapping_to <- c("Dragør Skole Syd",
                     "Sønderkærskolen",
                     "Fuglebjerg",
                     "Grønbro Hallen",
                     "Skolen ved Gurrevej",
                     "Lille Næstved Skole - Karrebæk",
                     "Kobberbakkeskolen - Sct. Jørge",
                     "Lille Næstved Skole - Herlufsh",
                     "Lille Næstved Skole - Hyllinge",
                     "Lille Næstved Skole - Karrebæk",
                     "Karlslunde Hallerne",
                     "Tune Hallerne",
                     "Hundige Hallen",
                     "Havdrup Idrætscenter",
                     "CSV-Skolen",
                     "Kroggårdsskolen",
                     "Rasmus Rask-Skolen",
                     "Bjerreby/Landet",
                     "Skibet Hallen Nord",
                     "Grejsdalen Nord",
                     "Multihallen v. Petersmindeskol",
                     "DGI-Huset Syd",
                     "Vinding Idræts Center Syd",
                     "CSV - Vejle Syd",
                     "TST Aktiv-Center, Tilst",
                     "Lystrup Hallen",
                     "Gjerlev Aktivitetshus",
                     "Asferg Træningshus",
                     "Idrætshallen",
                     "Sydstevnshallen",
                     "Munkekærhallen",
                     "Solrød Idrætscenter",
                     "Bjerreby/Landet",
                     "Vandel Nord",
                     "Kvartershuset Syd")


combined_name_mapping <- data.frame(from = name_mapping_from, to = name_mapping_to)

for (i in 1:length(name_mapping_from))
{
  idx <- which(characteristics_data[5] == name_mapping_from[i])
  characteristics_data[idx,5] = name_mapping_to[i]
}

combined_name_mapping
```

### Fill empty spaces between parties for joining later

```{r}
FV19TOTA <- fill(FV19TOTA, "Party", .direction = "down")
```

# Merge and filter

```{r}
characteristics_data <- characteristics_data %>% rename("Area" = "Valgdistrikt - navn")
rough_merged <- full_join(FV19TOTA, characteristics_data, by = "Area")
vote_characteristics <- subset(rough_merged, !is.na(rough_merged$Storkreds))
vote_characteristics <- vote_characteristics %>% rename("Polling_district" = "Area")
```

```{r}
head(vote_characteristics)
```

## Adding parties as columns

```{r}
characteristics_data_w_parties <- characteristics_data
characteristics_data_w_parties <- characteristics_data_w_parties[-c(1,2,3,4),]
#characteristics_data_w_parties

parties <- unique(vote_characteristics$Party)
parties <- parties[which(!is.na(parties))]

for (i in 1:length(parties))
{
  party_votes <- c()
  for (j in 5:length(characteristics_data$Opstillingskreds))
  {
    slc <- slice(characteristics_data,j)
    party_votes <- c(party_votes,subset(vote_characteristics,
                                        Party == parties[i] &
                                        Opstillingskreds == slc$Opstillingskreds &
                                        Polling_district == slc$Area &
                                        Storkreds == slc$Storkreds &
                                        !is.na(Votes))$Votes[1])
  }
  
  characteristics_data_w_parties[parties[i]] <- party_votes
}

head(characteristics_data_w_parties)
```

# Preparing for map data

```{r}
PD_w_votes <- characteristics_data_w_parties[-c(1,3,4,5,8,9,10,11,12,13,14,15,16,17,18,19,20)]

PD_w_votes$People <- as.integer(PD_w_votes$`Antal personer...6`) +
                         as.integer(PD_w_votes$`Antal personer...7`)

PD_w_votes <- PD_w_votes[-c(2,3)]

#Combined votes of parties that made it into parliament
PD_w_votes$TotalVotes <- PD_w_votes$`A. Socialdemokratiet` +
                             PD_w_votes$`B. Radikale Venstre` +
                             PD_w_votes$`C. Det Konservative Folkeparti` +
                             PD_w_votes$`D. Nye Borgerlige` +
                             PD_w_votes$`F. SF - Socialistisk Folkeparti` +
                             PD_w_votes$`I. Liberal Alliance` +
                             PD_w_votes$`O. Dansk Folkeparti` +
                             PD_w_votes$`V. Venstre, Danmarks Liberale Parti` +
                             PD_w_votes$`Ø. Enhedslisten - De Rød-Grønne` +
                             PD_w_votes$`Å. Alternativet`

for (i in 1:length(PD_w_votes$Opstillingskreds))
{
  split_string <- strsplit(PD_w_votes$Opstillingskreds[i], " ")[[1]]
  PD_w_votes$Opstillingskreds[i] <- paste(split_string[-c(1,length(split_string))],collapse=" ")
}

NDs = unique(PD_w_votes$Opstillingskreds)

collapsed_data <- slice(PD_w_votes,1)
for (i in 1:length(NDs))
{
  ss_df <- subset(PD_w_votes, Opstillingskreds == NDs[i])
  tmp_df <- ss_df[1,-1]
  
  for (j in 2:nrow(ss_df))
  {
    tmp_df <- tmp_df[1,] + ss_df[j,-1]
  }
  
  tmp_df$Opstillingskreds <- NDs[i]
  
  collapsed_data <- bind_rows(collapsed_data,tmp_df)
  
}
collapsed_data <- collapsed_data[-1,]
head(collapsed_data)
```

## Loading map data

```{r}
OpK <- read_sf("E:/pile_of_data/FYP4/DAGI/dagi_10m_nohist_l1.opstillingskreds/opstillingskreds.shp")
OpK <- st_transform(OpK, CRS("+init=epsg:3395"))
OpK <- st_zm(OpK, drop = TRUE, what = "ZM")

OpK <- OpK %>% rename("Opstillingskreds" = "navn")
```

### Fixing spelling inconsistencies

```{r}
name_mapping_from <- c("Aarhus Nord",
                       "Aarhus Øst",
                       "Aarhus Syd",
                       "Aarhus Vest")

name_mapping_to <- c("Århus Nord",
                     "Århus Øst",
                     "Århus Syd",
                     "Århus Vest")

combined_name_mapping <- data.frame(from = name_mapping_from, to = name_mapping_to)

for (i in 1:length(name_mapping_from))
{
  idx <- which(OpK[16]$Opstillingskreds == name_mapping_from[i])
  OpK[idx,16] = name_mapping_to[i]
}

combined_name_mapping
```

## Merging map data with dataset containing votes for all nomination districts

```{r}
OpK_merged <- full_join(OpK, collapsed_data, by = "Opstillingskreds")
#OpK_merged <- OpK_merged[-which(is.na(OpK_merged$`A. Socialdemokratiet`)),]
#OpK_merged <- OpK_merged[-which(is.na(OpK_merged$`opstilling`)),]
```

## Distorting the original shape file to create a cartogram shape file

```{r}
OpK_cont <- cartogram_cont(OpK_merged, "TotalVotes", itermax = 10)
```

### Result of distorting the shape, weighted by combined number of votes cast for parties that made it into parliament

```{r}
tm_shape(OpK_cont) + tm_polygons("TotalVotes", style= "jenks") +
  tm_layout(frame = FALSE, legend.position = c("right","top"))
```

# Adding election results to cartogram

```{r}
red_parties_sum <- OpK_cont$`A. Socialdemokratiet` +
                   OpK_cont$`B. Radikale Venstre` +
                   OpK_cont$`F. SF - Socialistisk Folkeparti` +
                   OpK_cont$`Ø. Enhedslisten - De Rød-Grønne` +
                   OpK_cont$`Å. Alternativet`

blue_parties_sum <- OpK_cont$`V. Venstre, Danmarks Liberale Parti` +
                    OpK_cont$`O. Dansk Folkeparti` +
                    OpK_cont$`C. Det Konservative Folkeparti` +
                    OpK_cont$`I. Liberal Alliance` +
                    OpK_cont$`D. Nye Borgerlige`
  
diff_vector <- red_parties_sum - blue_parties_sum
OpK_cont$RvsB <- diff_vector
```

## Styling the final plot

```{r}
main_plot <- ggplot() +
  geom_sf(data = OpK_cont, size = 0.5, aes(fill = RvsB)) +
  
  scale_fill_gradient2(low = "darkblue",
                       mid = "white",
                       high = "darkred",
                       midpoint = 0,
                       name = "R vs. B votes") +
  
  ggtitle("Vote distribution in nomination districts",
          subtitle = "Difference between number of red and blue votes") +
  
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        plot.title  = element_text(size = 20)) +
  
  coord_sf(xlim = c(900000, 1500000), ylim = c(7220000, 7880000), expand=FALSE)

bornholm_plot <- ggplot() +
  geom_sf(data = OpK_cont, size = 0.5, aes(fill = RvsB)) +
  
  scale_fill_gradient2(low = "darkblue",
                       mid = "white",
                       high = "darkred",
                       midpoint = 0,
                       guide = FALSE) +
  
  ggtitle("Bornholm") +
  
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        plot.title  = element_text(size = 10)) +
  
  coord_sf(xlim = c(1631000, 1695000), ylim = c(7322000, 7390000), expand=FALSE)

vp <- viewport(width = 0.25, height = 0.25, x = 0.57, y = 0.725)

#pdf("vote_distribution_map.pdf")

print(main_plot)
print(bornholm_plot, vp=vp)

#dev.off()
```

