---
title: "Work on 4 part 3"
author: "Andreas Møller Belsager"
date: "5/14/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(sf)
library(ggplot2)
library(xlsx)
library(dplyr)
library(tidyr)
library(tidyverse)
library(gridExtra)
library(gtable)
library(grid)
library(tmap)
library(cartogram)
```

```{r}
#load data, summarise rows for "Vest- og Sydsjælland" and "Østsjælland" into a single row called "Sjælland", and make a subset only containing the name of the 'Storkreds' and the geometry column
map_data <- read_sf("C:/Users/andre/OneDrive/Documents/ITU/fyp/4/DAGI/dagi_10m_nohist_l1.landsdel/landsdel.shp")
map_data <- summarise(group_by(map_data, navn))
map_data <- mutate(map_data, navn = na_if(navn, "Vest- og Sydsjælland"))
map_data <- mutate(map_data, navn = na_if(navn, "Østsjælland"))
map_data <- mutate(map_data, navn = replace_na(navn, "Sjælland"))
map_data <- summarise(group_by(map_data, navn))

# load file for scraped data, remove rows for parties that did not get any mandates in the 'Storkreds'
mandat_data <- read.xlsx2("C:/Users/andre/OneDrive/Documents/ITU/fyp/4/mandater.xlsx",1,stringsAsFactors = FALSE)
mandat_data <- filter(mandat_data, Mandater != "-")
mandat_data$Mandater <- as.integer(mandat_data$Mandater)
mandat_data <- mutate(mandat_data, navn = na_if(navn, ""))
mandat_data <- fill(mandat_data, navn, .direction = "down")

# join the two data frames
map_data_2 <- left_join(map_data, mandat_data, by = "navn")
map_data_2
```




Background layer (using map_data)


```{r}
map_data_3 <- map_data_2

# 1. make new column that has "red" if red party and "blue" if blue party
map_data_4 <- filter(map_data_3, Partier == "A. Socialdemokratiet" | Partier == "B. Radikale Venstre" | Partier == "F. SF - Socialistisk Folkeparti" | Partier == "Ø. Enhedslisten" | Partier == "Å. Alternativet")
map_data_4 <- mutate(map_data_4, block = "red")
map_data_4 <- summarise(group_by(map_data_4, navn, Partier, block))
map_data_4 <- st_drop_geometry(map_data_4)
map_data_3 <- left_join(map_data_3, map_data_4, by = c("navn", "Partier"))
map_data_3 <- mutate(map_data_3, block = replace_na(block, "blue"))

# 2. add the mandates for each "navn" for each of the blocks
map_data_3$block_mandates <- ave(map_data_3$Mandater, map_data_3$navn, map_data_3$block, FUN=sum)

# 3. remove the party-names column
map_data_3 <- summarise(group_by(map_data_3, navn, block, block_mandates))

# 4. check whether the blue block or the red block has won that "storkreds" or if it is a tie and add the result to a new column
winner_map_data <- map_data_3

winner_map_data$winning_mandates_number <- ave(winner_map_data$block_mandates, winner_map_data$navn, FUN=max)
winner_map_data <- mutate(winner_map_data, winning_block = identical(block_mandates, winning_mandates_number))
winner_map_data <- filter(winner_map_data, winning_block == TRUE)
winner_map_data <- summarise(group_by(winner_map_data, navn, block))

# if two successive rows have the same value in 'navn', replace TRUE with 'tie':
checkker <- summarise(group_by(winner_map_data, navn), tie = n()>1)
checkker <- st_drop_geometry(checkker)
winner_map_data <- left_join(winner_map_data, checkker, by = "navn")

replace_tie <- filter(winner_map_data, tie == TRUE)
replace_tie <- mutate(replace_tie, winner = "tie")
replace_tie <- st_drop_geometry(replace_tie)


# 5. add new column to map_data with the result of each 'Storkreds' and summarise
winner_map_data <- left_join(winner_map_data, replace_tie, by = "navn")
winner_map_data <- summarise(group_by(winner_map_data, navn, block.x, winner))
winner_map_data <- mutate(winner_map_data, winner = replace_na(winner, block.x))
winner_map_data <- summarise(group_by(winner_map_data, navn, winner))
winner_map_data
```



```{r}
winner_map <- ggplot(winner_map_data) + geom_sf(aes(fill=winner)) + scale_fill_manual(values=c("blue", "red", "yellow")
) + xlab("longtitude") + ylab("lattitude") + ggsave("winner_map2.png", width = 10, height = 10)
winner_map
```




Making the individual pie charts:

```{r}
bornholm_data <- filter(map_data_2, navn == "Bornholm")
byen_kobenhavn_data <- filter(map_data_2, navn == "Byen København")
fyn_data <- filter(map_data_2, navn == "Fyn")
kobenhavns_omegn_data <- filter(map_data_2, navn == "Københavns omegn")
nordjylland_data <- filter(map_data_2, navn == "Nordjylland")
nordsjaelland_data <- filter(map_data_2, navn == "Nordsjælland")
ostjylland_data <- filter(map_data_2, navn == "Østjylland")
sjaelland_data <- filter(map_data_2, navn == "Sjælland")
sydjylland_data <- filter(map_data_2, navn == "Sydjylland")
vestjylland_data <- filter(map_data_2, navn == "Vestjylland")
```



Bornholm

```{r}
bornholm_data <- bornholm_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(bornholm_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
bornholm_pie_chart <- ggplot(bornholm_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Bornholm") + ggsave("Bornholm_pie_chart.png")
bornholm_pie_chart
```

København By

```{r}
byen_kobenhavn_data <- byen_kobenhavn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(byen_kobenhavn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
byen_kobenhavn_pie_chart <- ggplot(byen_kobenhavn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Byen København") + ggsave("byen_kobenhavn_pie_chart.png")
byen_kobenhavn_pie_chart
```






Fyn

```{r}
fyn_data <- fyn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(fyn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
fyn_pie_chart <- ggplot(fyn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Fyn") + ggsave("fyn_pie_chart.png")
fyn_pie_chart
```


Københavns Omegn

```{r}
kobenhavns_omegn_data <- kobenhavns_omegn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(kobenhavns_omegn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
kobenhavns_omegn_pie_chart <- ggplot(kobenhavns_omegn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Københavns Omegn") + ggsave("kobenhavns_omegn_pie_chart.png")
kobenhavns_omegn_pie_chart
```


Nordjylland

```{r}
nordjylland_data <- nordjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordjylland_pie_chart <- ggplot(nordjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Nordjylland") + ggsave("nordjylland_pie_chart.png")
nordjylland_pie_chart
```


Nordsjælland

```{r}
nordsjaelland_data <- nordsjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordsjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordsjaelland_pie_chart <- ggplot(nordsjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Nordsjælland") + ggsave("nordsjælland_pie_chart.png")
nordsjaelland_pie_chart
```


Østjylland

```{r}
ostjylland_data <- ostjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(ostjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
ostjylland_pie_chart <- ggplot(ostjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Østjylland") + ggsave("ostjylland_pie_chart.png")
ostjylland_pie_chart
```


Sjælland

```{r}
sjaelland_data <- sjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sjaelland_pie_chart <- ggplot(sjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Sjælland") + ggsave("sjaelland_pie_chart.png")
sjaelland_pie_chart
```


Sydjylland

```{r}
sydjylland_data <- sydjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sydjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sydjylland_pie_chart <- ggplot(sydjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Sydjylland") + ggsave("sydjylland_pie_chart.png")
sydjylland_pie_chart
```



Vestjylland

```{r}
vestjylland_data <- vestjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(vestjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
vestjylland_pie_chart <- ggplot(vestjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5) + ggtitle("Vestjylland") + ggsave("vestjylland_pie_chart.png")
vestjylland_pie_chart
```



Pie chart grid with numbers

```{r}
bornholm_data <- bornholm_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(bornholm_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
bornholm_pie_chart <- ggplot(bornholm_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

byen_kobenhavn_data <- byen_kobenhavn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(byen_kobenhavn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
byen_kobenhavn_pie_chart <- ggplot(byen_kobenhavn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

fyn_data <- fyn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(fyn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
fyn_pie_chart <- ggplot(fyn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

kobenhavns_omegn_data <- kobenhavns_omegn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(kobenhavns_omegn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
kobenhavns_omegn_pie_chart <- ggplot(kobenhavns_omegn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

nordjylland_data <- nordjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordjylland_pie_chart <- ggplot(nordjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

nordsjaelland_data <- nordsjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordsjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordsjaelland_pie_chart <- ggplot(nordsjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

ostjylland_data <- ostjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(ostjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
ostjylland_pie_chart <- ggplot(ostjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

sjaelland_data <- sjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sjaelland_pie_chart <- ggplot(sjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

sydjylland_data <- sydjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sydjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sydjylland_pie_chart <- ggplot(sydjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)

vestjylland_data <- vestjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(vestjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
vestjylland_pie_chart <- ggplot(vestjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF")) + geom_text(aes(y = ypos, label = Mandater), color = "white", size=5)



g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(ostjylland_pie_chart)

p3 <- grid.arrange(arrangeGrob(
  bornholm_pie_chart + theme(legend.position="none") + labs(caption = "Bornholm"), 
  byen_kobenhavn_pie_chart + theme(legend.position="none") + labs(caption = "Byen København"),
  fyn_pie_chart + theme(legend.position="none") + labs(caption = "Fyn"), 
  kobenhavns_omegn_pie_chart + theme(strip.text = , legend.position="none") + labs(caption = "Københavns Omegn"), 
  nordjylland_pie_chart + theme(legend.position="none") + labs(caption = "Nordjylland"), 
  nordsjaelland_pie_chart + theme(legend.position="none") + labs(caption = "Nordsjælland"), 
  ostjylland_pie_chart + theme(legend.position="none") + labs(caption = "Østjylland"), 
  sjaelland_pie_chart + theme(legend.position="none") + labs(caption = "Sjælland"), 
  sydjylland_pie_chart + theme(legend.position="none") + labs(caption = "Sydjylland"), 
  vestjylland_pie_chart + theme(legend.position="none") + labs(caption = "Vestjylland"),
                         nrow=5),
             mylegend, ncol=2,heights=c(75, 1), widths=c(1,1))
```



Pie chart grid without numbers

```{r}
bornholm_data <- bornholm_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(bornholm_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
bornholm_pie_chart <- ggplot(bornholm_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#6699FF"))

byen_kobenhavn_data <- byen_kobenhavn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(byen_kobenhavn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
byen_kobenhavn_pie_chart <- ggplot(byen_kobenhavn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF"))

fyn_data <- fyn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(fyn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
fyn_pie_chart <- ggplot(fyn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF"))

kobenhavns_omegn_data <- kobenhavns_omegn_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(kobenhavns_omegn_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
kobenhavns_omegn_pie_chart <- ggplot(kobenhavns_omegn_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF"))

nordjylland_data <- nordjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordjylland_pie_chart <- ggplot(nordjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#FF6666", "#000099", "#FF0000", "#6699FF"))

nordsjaelland_data <- nordsjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(nordsjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
nordsjaelland_pie_chart <- ggplot(nordsjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF"))

ostjylland_data <- ostjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(ostjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
ostjylland_pie_chart <- ggplot(ostjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF"))

sjaelland_data <- sjaelland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sjaelland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sjaelland_pie_chart <- ggplot(sjaelland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("green", "#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "#000099", "#FF0000", "#6699FF"))

sydjylland_data <- sydjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(sydjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
sydjylland_pie_chart <- ggplot(sydjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#336666", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF"))

vestjylland_data <- vestjylland_data %>% 
  arrange(desc(Partier)) %>%
  mutate(prop = Mandater / sum(vestjylland_data$Mandater) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
vestjylland_pie_chart <- ggplot(vestjylland_data, aes(x="", y=prop, fill=Partier)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + scale_fill_manual(values=c("#CC0000", "#FF3399", "dark green", "#FF6666", "orange", "#000099", "#FF0000", "#6699FF"))



g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(ostjylland_pie_chart)

p3 <- grid.arrange(arrangeGrob(
  bornholm_pie_chart + theme(legend.position="none") + labs(caption = "Bornholm"), 
  byen_kobenhavn_pie_chart + theme(legend.position="none") + labs(caption = "Byen København"),
  fyn_pie_chart + theme(legend.position="none") + labs(caption = "Fyn"), 
  kobenhavns_omegn_pie_chart + theme(strip.text = , legend.position="none") + labs(caption = "Københavns Omegn"), 
  nordjylland_pie_chart + theme(legend.position="none") + labs(caption = "Nordjylland"), 
  nordsjaelland_pie_chart + theme(legend.position="none") + labs(caption = "Nordsjælland"), 
  ostjylland_pie_chart + theme(legend.position="none") + labs(caption = "Østjylland"), 
  sjaelland_pie_chart + theme(legend.position="none") + labs(caption = "Sjælland"), 
  sydjylland_pie_chart + theme(legend.position="none") + labs(caption = "Sydjylland"), 
  vestjylland_pie_chart + theme(legend.position="none") + labs(caption = "Vestjylland"),
                         nrow=5),
             mylegend, ncol=2,heights=c(75, 1), widths=c(1,1))
```




Making the distortion map

```{r}
distortion_data <- map_data_2
distortion_data <- st_zm(distortion_data)
distortion_data$sum_mandates <- ave(distortion_data$Mandater, distortion_data$navn, FUN = sum)
distortion_data <- summarise(group_by(distortion_data, navn, sum_mandates))
distortion_data
```


Making a continuous area cartogram using the 'Dougenik et al. 1985'-algorithm (note this can take some time to load)

```{r}
OpK_cont <- cartogram_cont(distortion_data, "sum_mandates", itermax = 10)
```

Plotting using the tmap-library

```{r}
tm_shape(OpK_cont) + tm_polygons("sum_mandates", style= "jenks") +
  tm_layout(title = 'Distorted map',frame = FALSE, legend.position = c(0.75,0.5), title.position = c(0.5,0.9))
```






